Does online masked priming pass the test?\\ The effects of prime exposure duration on masked identity priming

### 2021-11-03 MaskedPriming_revision_accepted.Rmd
Move old documents to different directory, make final Rmd and tex files

  - id            : "1"
    institution   : "Bournemouth University, Bournemouth, UK"
  - id            : "2"
    institution   : "Universidad Antonio de Nebrija, Madrid, Spain"
  - id            : "3"
    institution   : "DePaul University, Chicago, USA"
  - id            : "4"
    institution   : "California State University San Bernardino, Palm Desert Campus, USA"
  - id            : "5"
    institution   : "Universitat de València, Valencia, Spain"
note: "\\clearpage"
authornote: |

@@

keywords          : "Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration"
wordcount         : "7916"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
csl               : "apa.csl"
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
bibliography: ["references.bib", "r-references.bib"]
nocite: |
  - @ratcliff2002
appendix:
  - "Appendix_A.Rmd"
  - "Appendix_B.Rmd"
editor_options: 
  chunk_output_type: console
---

@@

>>>>

  - id            : "1"
    institution   : "Bournemouth University, Bournemouth, UK"
  - id            : "2"
    institution   : "Centro de Investigación Nebrija en Cognición (CINC), Universidad Nebrija, Madrid, Spain"
  - id            : "3"
    institution   : "DePaul University, Chicago, USA"
  - id            : "4"
    institution   : "California State University San Bernardino, Palm Desert Campus, USA"
  - id            : "5"
    institution   : "Universitat de València, Valencia, Spain"
note: "\\clearpage"
authornote: |

@@

keywords          : "Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration"
wordcount         : "7192"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
csl               : "apa.csl"
documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf:
    keep_tex: TRUE
bibliography: ["references.bib", "r-references.bib"]
nocite: |
  - @ratcliff2002
appendix:
  - "Appendix_A.Rmd"
  - "Appendix_B.Rmd"
editor_options: 
  chunk_output_type: console
---

@@

```{r echo = FALSE, results = 'asis', cache = FALSE}
#papaja::render_appendix('Appendix_A.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
#papaja::render_appendix('Appendix_B.Rmd')
```
